
    \foldertitle{SVAR}{Structural vector autoregressions: SVAR objects and functions}{SVAR/Contents}

	SVAR methods:
 
 \paragraph{Constructor}
 
 \begin{itemize}
 \item
   \href{SVAR/SVAR}{\texttt{SVAR}} - Convert reduced-form VAR to
   structural VAR.
 \end{itemize}
 
 SVAR objects can call any of the \href{VAR/Contents}{VAR} functions. In
 addition, the following functions are available for SVAR objects.
 
 \paragraph{Getting information about SVAR objects}
 
 \begin{itemize}
 \item
   \href{SVAR/fprintf}{\texttt{fprintf}} - Format SVAR as a model code
   and write to text file.
 \item
   \href{SVAR/get}{\texttt{get}} - Query SVAR object properties.
 \item
   \href{SVAR/sprintf}{\texttt{sprintf}} - Format SVAR as a model code
   and write to text string.
 \end{itemize}
 
 \paragraph{Simulation}
 
 \begin{itemize}
 \item
   \href{SVAR/srf}{\texttt{srf}} - Shock (impulse) response function.
 \end{itemize}
 
 \paragraph{Stochastic properties}
 
 \begin{itemize}
 \item
   \href{SVAR/fevd}{\texttt{fevd}} - Forecast error variance
   decomposition for SVAR variables.
 \end{itemize}
 
 \paragraph{Manipulating SVAR objects}
 
 \begin{itemize}
 \item
   \href{SVAR/sort}{\texttt{sort}} - Sort SVAR parameterisations by
   squared distance of shock reponses to median.
 \end{itemize}
 
 See help on \href{VAR/Contents}{VAR} objects for other functions
 available.
 
 \paragraph{Getting on-line help on SVAR functions}
 
 \begin{verbatim}
 help SVAR
 help SVAR/function_name
 \end{verbatim}
 
 \paragraph{Getting on-line help on SVAR functions that are inherited
 from VARs}
 
 \begin{verbatim}
 help VAR
 help VAR/function_name
 \end{verbatim}



