

    \filetitle{fevd}{Forecast error variance decomposition for model variables}{model/fevd}

	\paragraph{Syntax}
 
 \begin{verbatim}
 [X,Y,List,A,B] = fevd(M,Range,...)
 [X,Y,List,A,B] = fevd(M,NPer,...)
 \end{verbatim}
 
 \paragraph{Input arguments}
 
 \begin{itemize}
 \item
   \texttt{M} {[} model {]} - Model object for which the decomposition
   will be computed.
 \item
   \texttt{Range} {[} numeric {]} - Decomposition date range with the
   first date beign the first forecast period.
 \item
   \texttt{NPer} {[} numeric {]} - Number of periods for which the
   decomposition will be computed.
 \end{itemize}
 
 \paragraph{Output arguments}
 
 \begin{itemize}
 \item
   \texttt{X} {[} namedmat \textbar{} numeric {]} - Array with the
   absolute contributions of individual shocks to total variance of each
   variables.
 \item
   \texttt{Y} {[} namedmat \textbar{} numeric {]} - Array with the
   relative contributions of individual shocks to total variance of each
   variables.
 \item
   \texttt{List} {[} cellstr {]} - List of variables in rows of the
   \texttt{X} an \texttt{Y} arrays, and shocks in columns of the
   \texttt{X} and \texttt{Y} arrays.
 \item
   \texttt{A} {[} struct {]} - Database with the absolute contributions
   converted to time series.
 \item
   \texttt{B} {[} struct {]} - Database with the relative contributions
   converted to time series.
 \end{itemize}
 
 \paragraph{Options}
 
 \begin{itemize}
 \item
   \texttt{'output='} {[} \emph{`namedmat'} \textbar{} numeric {]} -
   Output matrices \texttt{X} and \texttt{Y} will be either namedmat
   objects or plain numeric arrays; if the option \texttt{'select='} is
   used, \texttt{'output='} is always \texttt{'namedmat'}.
 \item
   \texttt{'select='} {[} char \textbar{} cellstr {]} - Return FEVD for
   selected variables and/or shocks only; \texttt{Inf} means all
   variables. This option does not apply to the output databases,
   \texttt{A} and \texttt{B}.
 \end{itemize}
 
 \paragraph{Description}
 
 \paragraph{Example}


