

    \filetitle{model}{Create new model object based on model file}{model/model}

	\paragraph{Syntax}
 
 \begin{verbatim}
 m = model(fname,...)
 m = model(m,...)
 \end{verbatim}
 
 \paragraph{Input arguments}
 
 \begin{itemize}
 \item
   \texttt{fname} {[} char \textbar{} cellstr {]} - Name(s) of the model
   file(s) that will loaded and converted to a new model object.
 \item
   \texttt{m} {[} model {]} - Existing model object that will be rebuilt
   as if from a model file.
 \end{itemize}
 
 \paragraph{Output arguments}
 
 \begin{itemize}
 \item
   \texttt{m} {[} model {]} - New model object based on the input model
   code file or files.
 \end{itemize}
 
 \paragraph{Options}
 
 \begin{itemize}
 \item
   \texttt{'multiple='} {[} true \textbar{} \emph{false} {]} - Allow each
   variable, shock, or parameter name to be declared (and assigned) more
   than once in the model file.
 \item
   \texttt{'assign='} {[} struct \textbar{} \emph{empty} {]} - Assign
   model parameters and/or steady states from this database at the time
   the model objects is being created.
 \item
   \texttt{'baseYear='} {[} numeric \textbar{} \emph{2000} {]} - Base
   year for constructing deterministic time trends.
 \item
   \texttt{'comment='} {[} char \textbar{} \emph{empty} {]} - Text
   comment attached to the model object.
 \item
   \texttt{'declareParameters='} {[} \emph{\texttt{true}} \textbar{}
   \texttt{false} {]} - If \texttt{false}, skip parameter declaration in
   the model file, and determine the list of parameters automatically as
   names found in equations but not declared.
 \item
   \texttt{'epsilon='} {[} numeric \textbar{} \emph{eps\^{}(1/4)} {]} -
   The minimum relative step size for numerical differentiation.
 \item
   \texttt{'linear='} {[} \texttt{true} \textbar{} \emph{\texttt{false}}
   {]} - Indicate linear models.
 \item
   \texttt{'removeLeads='} {[} \texttt{true} \textbar{}
   \emph{\texttt{false}} {]} - Remove all leads from the state-space
   vector, keep included only current dates and lags.
 \item
   \texttt{'sstateOnly='} {[} \texttt{true} \textbar{}
   \emph{\texttt{false}} {]} - Read in only the steady-state versions of
   equations (if available).
 \item
   \texttt{'std='} {[} numeric \textbar{} \emph{1} for linear models
   \textbar{} \emph{0.01} for non-linear models {]} - Default standard
   deviation for model shocks.
 \item
   \texttt{'userdata='} {[} \ldots{} \textbar{} \emph{empty} {]} - Attach
   user data to the model object.
 \end{itemize}
 
 \paragraph{Description}
 
 \subparagraph{Loading a model file}
 
 The \texttt{model} function can be used to read in a
 \href{modellang/Contents}{model file} named \texttt{fname}, and create a
 model object \texttt{m} based on the model file. You can then work with
 the model object in your own m-files, using using the IRIS
 \href{model/Contents}{model functions} and standard Matlab functions.
 
 If \texttt{fname} is a cell array of more than one filenames then all
 files are combined together (in order of appearance).
 
 \subparagraph{Re-building an existing model object}
 
 The only instance where you may need to call a model function on an
 existing model object is to change the \texttt{'removeLeads='} option.
 Of course, you can always achieve the same by loading the original model
 file.
 
 \paragraph{Example 1}
 
 Read in a model code file named \texttt{my.model}, and declare the model
 as linear:
 
 \begin{verbatim}
 m = model('my.model','linear',true);
 \end{verbatim}
 
 \paragraph{Example 2}
 
 Read in a model code file named \texttt{my.model}, declare the model as
 linear, and assign some of the model parameters:
 
 \begin{verbatim}
 m = model('my.model','linear=',true,'assign=',P);
 \end{verbatim}
 
 Note that this is equivalent to
 
 \begin{verbatim}
 m = model('my.model','linear=',true);
 m = assign(m,P);
 \end{verbatim}
 
 unless some of the parameters passed in to the \texttt{model} fuction
 are needed to evaluate \href{modellang/if}{\texttt{if}} or
 \href{modellang/switch}{\texttt{!switch}} expressions.


