

    \filetitle{system}{System matrices before model is solved}{model/system}

	\paragraph{Syntax}
 
 \begin{verbatim}
 [A,B,C,D,F,G,H,J,List,NF] = system(M)
 \end{verbatim}
 
 \paragraph{Input arguments}
 
 \begin{itemize}
 \item
   \texttt{M} {[} model {]} - Model object whose system matrices will be
   returned.
 \end{itemize}
 
 \paragraph{Output arguments}
 
 \begin{itemize}
 \item
   \texttt{A} {[} numeric {]} - Matrix at the vector of expectations in
   the transition equation.
 \item
   \texttt{B} {[} numeric {]} - Matrix at current vector in the
   transition equations.
 \item
   \texttt{C} {[} numeric {]} - Constant vector in the transition
   equations.
 \item
   \texttt{D} {[} numeric {]} - Matrix at transition shocks in the
   transition equations.
 \item
   \texttt{F} {[} numeric {]} - Matrix at measurement variables in the
   measurement equations.
 \item
   \texttt{G} {[} numeric {]} - Matrix at predetermined transition
   variables in the measurement variables.
 \item
   \texttt{H} {[} numeric {]} - Constant vector in the measurement
   equations.
 \item
   \texttt{J} {[} numeric {]} - Matrix at measurement shocks in the
   measurement equations.
 \item
   \texttt{List} {[} cell {]} - Lists of measurement variables,
   transition variables includint their auxiliary lags and leads, and
   shocks as they appear in the rows and columns of the system matrices.
 \item
   \texttt{NF} {[} numeric {]} - Number of non-predetermined
   (forward-looking) transition variables.
 \end{itemize}
 
 \paragraph{Options}
 
 \begin{itemize}
 \item
   \texttt{'linear='} {[} \emph{\texttt{'auto'}} \textbar{} \texttt{true}
   \textbar{} \texttt{false} {]} - Compute the model using a linear
   approach, i.e.~differentiating around zero and not the currently
   assigned steady state.
 \item
   \texttt{'select='} {[} \emph{\texttt{true}} \textbar{} \texttt{false}
   {]} - Automatically detect which equations need to be
   re-differentiated based on parameter changes from the last time the
   system matrices were calculated.
 \end{itemize}
 
 \paragraph{Description}
 
 The system before the model is solved has the following form:
 
 \begin{verbatim}
 A E[xf;xb] + B [xf(-1);xb(-1)] + C + D e = 0
 
 F y + G xb + H + J e = 0
 \end{verbatim}
 
 where \texttt{E} is a conditional expectations operator, \texttt{xf} is
 a vector of non-predetermined (forward-looking) transition variables,
 \texttt{xb} is a vector of predetermined (backward-looking) transition
 variables, \texttt{y} is a vector of measurement variables, and
 \texttt{e} is a vector of transition and measurement shocks.
 
 \paragraph{Example}


