

    \filetitle{xsf}{Power spectrum and spectral density of model variables}{model/xsf}

	\paragraph{Syntax}
 
 \begin{verbatim}
 [S,D,List] = xsf(M,Freq,...)
 [S,D,List,Freq] = xsf(M,NFreq,...)
 \end{verbatim}
 
 \paragraph{Input arguments}
 
 \begin{itemize}
 \item
   \texttt{M} {[} model {]} - Model object.
 \item
   \texttt{Freq} {[} numeric {]} - Vector of frequencies at which the
   XSFs will be evaluated.
 \item
   \texttt{NFreq} {[} numeric {]} - Total number of requested
   frequencies; the frequencies will be evenly spread between 0 and
   \texttt{pi}.
 \end{itemize}
 
 \paragraph{Output arguments}
 
 \begin{itemize}
 \item
   \texttt{S} {[} namedmat \textbar{} numeric {]} - Power spectrum
   matrices.
 \item
   \texttt{D} {[} namedmat \textbar{} numeric {]} - Spectral density
   matrices.
 \item
   \texttt{List} {[} cellstr {]} - List of variable in order of
   appearance in rows and columns of \texttt{S} and \texttt{D}.
 \item
   \texttt{Freq} {[} numeric {]} - Vector of frequencies at which the
   XSFs has been evaluated.
 \end{itemize}
 
 \paragraph{Options}
 
 \begin{itemize}
 \item
   \texttt{'applyTo='} {[} cellstr \textbar{} char \textbar{}
   \emph{\texttt{Inf}} {]} - List of variables to which the option
   \texttt{'filter='} will be applied; \texttt{Inf} means all variables.
 \item
   \texttt{'filter='} {[} char \textbar{} \emph{empty} {]} - Linear
   filter that is applied to variables specified by `applyto'.
 \item
   \texttt{'nFreq='} {[} numeric \textbar{} \emph{\texttt{256}} {]} -
   Number of equally spaced frequencies over which the `filter' is
   numerically integrated.
 \item
   \texttt{'output='} {[} \emph{\texttt{'namedmat'}} \textbar{}
   \texttt{'numeric'} {]} - Output matrices \texttt{S} and \texttt{F}
   will be either namedmat objects or plain numeric arrays; if the option
   \texttt{'select='} is used, \texttt{'output='} is always a namedmat
   object.
 \item
   \texttt{'progress='} {[} \texttt{true} \textbar{}
   \emph{\texttt{false}} {]} - Display progress bar on in the command
   window.
 \item
   \texttt{'select='} {[} cellstr \textbar{} \emph{\texttt{Inf}} {]} -
   Return XSF for selected variables only; \texttt{Inf} means all
   variables.
 \end{itemize}
 
 \paragraph{Description}
 
 \paragraph{Example}


