---
title: "preparing results of forecast experiment"
author: "Dirk Ulbricht"
date: "Tuesday, January 13, 2015"
output: pdf_document
---

Not all of the forecasts are actually diffrent from the autoregression. This is the case whenever bma can not detect a signifcant lag of the other explanatory variable than the endogenous. Thus, in a first step, we have to identify those models that are actually useful beyond the AR model. 

First, however, we have to sort out those models, that could not be employed all periods due to zeros. Change rate transformations are not possible, if zeros appear in the denominator, and the models will therefore automatically not employed. 

```{r getting a list of all useful models,eval=T,echo=F}
DirCode='h:/git/bubblesbreakdowns'
load(paste(DirCode,'/Results/IPT hor 12 recursive.RData',sep=''))
# zero eliminated modelsK
N_mod_vint=sapply(forecast.all,function(x) nrow(x))
min.mod=which.min(N_mod_vint)
min.mod.names=as.character(forecast.all[[min.mod]]$names)
Nvint=length(forecast.all)
Notin=matrix(NA,Nvint,10)
for (vint in 1:Nvint){
        test=as.character(forecast.all[[vint]]$names)
        notin=!test%in%min.mod.names
        n=length(test[notin])
        if (n>0){
            Notin[vint,1:n]=test[notin]      
        }
}
# Notin contains all models that do not appear in all models
eliminate=as.vector(Notin)
eliminate=eliminate[is.na(eliminate)==F]
eliminate=unique(eliminate)

 for (vint in 1:Nvint){
        del=forecast.all[[vint]]$names%in%eliminate
        forecast.all[[vint]]=forecast.all[[vint]][!del,]
        
}  
text=paste(eliminate,colapse='',sep='')
```
```{r,echo=FALSE}
useful=sapply(forecast.all,function(x) x$useful)
useful.ind=rowSums(useful)==Nvint
useful.nvint=rowSums(useful)
use.ful.models=colSums(useful)
plot(use.ful.models,main='number of useful models\n each vintages',xlab='vintage',ylab='number of useful models',type='l')
hist(useful.nvint,main='histogram of how many\n vintages each model is useful',ylab='number of models',xlab='number of vintages when useful')
```

The models droped are `r text` for containing zeros at a certain point in time.
Furthermore, `r Nvint-sum(useful.ind)` models had to be dropped, as none of the lags of the exogenous explanatory variable has been significant at one point in time. 

