

    \filetitle{irisset}{Change configurable IRIS options}{config/irisset}

	\paragraph{Syntax}
 
 \begin{verbatim}
 irisset(Option,Value)
 irisset(Option,Value,Option,Value,...)
 \end{verbatim}
 
 \paragraph{Input arguments}
 
 \begin{itemize}
 \item
   \texttt{Option} {[} char {]} - Name of the IRIS configuration option
   that will be modified.
 \item
   \texttt{Value} {[} \ldots{} {]} - New value that will be assigned to
   the option.
 \end{itemize}
 
 \paragraph{Modifiable IRIS configuration options}
 
 \subparagraph{Dates and formats}
 
 \begin{itemize}
 \item
   \texttt{'dateFormat='} {[} char \textbar{} \emph{`YPF'} {]} - Date
   format used to display dates in the command window, CSV databases, and
   reports. Note that the default date format for graphs is controlled by
   the \texttt{'plotdateformat='} option. The default `YFP' means that
   the year, frequency letter, and period is displayed. See also help on
   \href{dates/dat2str}{\texttt{dat2str}} for more date formatting
   details. The \texttt{'dateformat='} option is also found in many IRIS
   functions whenever it is relevant, and can be used to overwrite the
   \texttt{'irisset='} settings.
 \item
   \texttt{'freqLetters='} {[} char \textbar{} \emph{`YHQBM'} {]} - Five
   letters used to represent the five possible frequencies of the IRIS
   dates: yearly, half-yearly, quarterly, bi-monthly, and monthly, such
   as the `Q' in `2010Q1' denoting.
 \item
   \texttt{'months='} {[} cellstr \textbar{}
   \emph{\{`January',\ldots{},`December'\}} {]} - Twelve strings
   representing the names of the twelve months. This option can be used
   whenever you want to replace the default English names with your local
   language. .
 \item
   \texttt{'plotDateFormat='} {[} char \textbar{} \emph{`Y:P'} {]} - Date
   format used to display dates in graphs including graphs in reports.
   The default is `Y:P', which is different from the
   \texttt{'dateformat='} option.
 \item
   \texttt{'tseriesFormat='} {[} char \textbar{} \emph{empty} {]} -
   Format string for displaying time series data on the screen. See help
   on the Matlab \texttt{sprintf} function for how to set up format
   strings. If empty the default format of the \texttt{num2str} function
   is used.
 \item
   \texttt{tseriesMaxWSpace='} {[} numeric \textbar{} \emph{\texttt{5}}
   {]} - Maximum number of white spaces printed between individual
   columns of a multivariate tseries object on the screen.
 \item
   \texttt{'standinMonth='} {[} \emph{`first'} \textbar{} `last'
   \textbar{} numeric {]} - This option specifies which month will be
   used to represent lower-frequency periods (such as a quarters) when a
   month-displaying format is used in \texttt{'dateformat='}.
 \end{itemize}
 
 \subparagraph{External tools used by IRIS}
 
 \begin{itemize}
 \item
   \texttt{'pdflatexPath='} {[} char {]} - Location of the
   \texttt{pdflatex.exe} program. This program is called to compile
   report and publish m-files. By default, IRIS attempts to locate
   \texttt{pdflatex.exe} by running TeX's \texttt{kpsewhich}, and
   \texttt{which} on Unix platforms.
 \item
   \texttt{'epstopdfPath='} {[} char {]} - Location of the
   \texttt{epstopdf.exe} program. This program is called to convert EPS
   graphics files to PDFs in reports.
 \end{itemize}
 
 \subparagraph{Other options}
 
 \begin{itemize}
 \item
   \texttt{'extensions='} {[} cellstr \textbar{}
   \emph{\{`model','s',`q'\}} {]} - List of extensions that are
   automatically associated with the Matlab editor. The advantage of such
   associations is that the IRIS \href{modellang/Contents}{model files},
   \href{sstatelang/Contents}{steady-state files}, and
   \href{qreport/Contents}{quick-report} files get syntax-highlighted.
 \end{itemize}
 
 \paragraph{Description}
 
 \paragraph{Example}


