

    \filetitle{figure}{Start new figure}{report/figure}

	\paragraph{Syntax}
 
 \begin{verbatim}
 P.figure(Caption,...)
 \end{verbatim}
 
 \paragraph{Syntax to capture an existing figure window}
 
 This is an obsolete syntax, and will be removed from IRIS in a future
 release. Use \url{report/userfigure} instead.
 
 \begin{verbatim}
 P.figure(Caption,H,...)
 \end{verbatim}
 
 \paragraph{Input arguments}
 
 \begin{itemize}
 \item
   \texttt{P} {[} struct {]} - Report object created by the
   \href{report/new}{\texttt{report.new}} function.
 \item
   \texttt{Caption} {[} char \textbar{} cellstr {]} - Title or a cell
   array with title and subtitle displayed at the top of the figure; see
   Description for splitting the title or subtitle into multiple lines.
 \item
   \texttt{H} {[} numeric {]} - See help on \url{report/userfigure}.
 \end{itemize}
 
 \paragraph{Options}
 
 \begin{itemize}
 \item
   \texttt{'captionTypeface='} {[} cellstr \textbar{} char \textbar{}
   \emph{\texttt{'\textbackslash{}large\textbackslash{}bfseries'}} {]} -
   LaTeX format commands for typesetting the figure caption; the
   subcaption format can be entered as the second cell in a cell array.
 \item
   \texttt{'close='} {[} \emph{\texttt{true}} \textbar{} \texttt{false}
   {]} - (Inheritable from parent objects) Close Matlab the underlying
   figure window when finished.
 \item
   \texttt{'separator='} {[} char \textbar{}
   \emph{\texttt{'\textbackslash{}medskip\textbackslash{}par'}} {]} -
   (Inheritable from parent objects) LaTeX commands that will be inserted
   after the figure.
 \item
   \texttt{'figureOptions='} {[} cell \textbar{} \emph{empty} {]} -
   Figure options that will be applied to the figure handle after all
   graphs are drawn.
 \item
   \texttt{'figureScale='} {[} numeric \textbar{} \emph{\texttt{0.85}}
   {]} - (Inheritable from parent objects) Scale of the figure in the
   LaTeX document.
 \item
   \texttt{'footnote='} {[} char \textbar{} \emph{empty} {]} - Footnote
   at the figure title; only shows if the title is non-empty.
 \item
   \texttt{'sideways='} {[} \texttt{true} \textbar{}
   \emph{\texttt{false}} {]} - (Inheritable from parent objects) Print
   the table rotated by 90 degrees.
 \item
   \texttt{'style='} {[} struct \textbar{} \emph{empty} {]} - Apply this
   cascading style structure to the figure; see
   \href{qreport/qstyle}{\texttt{qstyle}}.
 \item
   \texttt{'subplot='} {[} numeric \textbar{} \emph{\texttt{'auto'}} {]}
   - (Inheritable from parent objects) Subplot division of the figure.
 \item
   \texttt{'typeface='} {[} char \textbar{} \emph{empty} {]} - (Not
   inheritable from parent objects) LaTeX code specifying the typeface
   for the figure as a whole; it must use the declarative forms (such as
   \texttt{\textbackslash{}itshape}) and not the command forms (such as
   \texttt{\textbackslash{}textit\{...\}}).
 \item
   \texttt{'visible='} {[} \texttt{true} \textbar{} \emph{\texttt{false}}
   {]} - (Inheritable from parent objects) Visibility of the underlying
   Matlab figure window.
 \end{itemize}
 
 \paragraph{Generic options}
 
 See help on \href{report/Contents}{generic options} in report objects.
 
 \paragraph{Description}
 
 Figures are top-level report objects and cannot be nested within other
 report objects, except \href{report/align}{\texttt{align}}. Figure
 objects can have the following types of children:
 
 \begin{itemize}
 \item
   \href{report/graph}{\texttt{graph}};
 \item
   \href{report/empty}{\texttt{empty}}.
 \end{itemize}
 
 \subparagraph{Titles and subtitles}
 
 The input argument \texttt{Caption} can be either a text string, or a
 1-by-2 cell array of strings. In the latter case, the first cell will be
 printed as a title, and the second cell will be printed as a subtitle.
 
 To split the title or subtitle into multiple lines, use the following
 LaTeX commands wrapped in curly brackets:
 \texttt{\{\textbackslash{}\textbackslash{}\}} or
 \texttt{\{\textbackslash{}\textbackslash{}{[}Xpt{]}\}}, where \texttt{X}
 is the width of an extra vertical space (in points) added between the
 respective lines.
 
 \paragraph{Example}


