

    \filetitle{graph}{Add graph to figure}{report/graph}

	\paragraph{Syntax}
 
 \begin{verbatim}
 P.graph(Caption,...)
 \end{verbatim}
 
 \paragraph{Input arguments}
 
 \begin{itemize}
 \item
   \texttt{P} {[} struct {]} - Report object created by the
   \href{report/new}{\texttt{report.new}} function.
 \item
   \texttt{Caption} {[} char \textbar{} cellstr {]} - Title, or cell
   array with title and subtitle, displayed at the top of the graph.
 \end{itemize}
 
 \paragraph{Options}
 
 \begin{itemize}
 \item
   \texttt{'axesOptions='} {[} cell \textbar{} \emph{empty} {]} -
   (Inheritable) Options executed by calling \texttt{set} on the axes
   handle before running \texttt{'postProcess='}.
 \item
   \texttt{'dateFormat='} {[} char \textbar{} \emph{\texttt{'YYYY:P'}}
   {]} - (Inheritable) Date format string, see help on
   \href{dates/dat2str}{\texttt{dat2str}}.
 \item
   \texttt{'dateTick='} {[} numeric \textbar{} \emph{\texttt{Inf}} {]} -
   (Inheritable) Date tick spacing.
 \item
   \texttt{'legend='} {[} \emph{\texttt{false}} \textbar{} \texttt{true}
   {]} - (Inheritable) Add legend to the graph.
 \item
   \texttt{'legendLocation='} {[} char \textbar{} \emph{\texttt{'best'}}
   \textbar{} \texttt{'bottom'}{]} - (Inheritable) Location of the legend
   box; see help on \texttt{legend} for values available.
 \item
   \texttt{'postProcess='} {[} char \textbar{} \emph{empty} {]} -
   (Inheritable) String with Matlab commands executed after the graph has
   been drawn and styled; the commands have access to variable
   \texttt{H}, a handle to the current axes object.
 \item
   \texttt{'preProcess='} {[} char \textbar{} \emph{empty} {]} -
   (Inheritable) String with Matlab commands executed before the graph
   has been drawn and styled; the commands have access to variable
   \texttt{H}, a handle to the current axes object.
 \item
   \texttt{'range='} {[} numeric \textbar{} \emph{\texttt{Inf}} {]} -
   (Inheritable) Graph range.
 \item
   \texttt{'rhsAxesOptions='} {[} cell \textbar{} \emph{empty} {]} -
   (Inheritable) Options executed by calling \texttt{set} on the RHS axes
   handle before running \texttt{'postProcess='}.
 \item
   \texttt{'style='} {[} struct \textbar{} \emph{empty} {]} -
   (Inheritable) Apply this style structure to the graph and its
   children; see help on \href{qreport/qstyle}{\texttt{qstyle}}.
 \item
   \texttt{'tight='} {[} \emph{\texttt{true}} \textbar{} \texttt{false}
   {]} - (Inheritable) Set the y-axis limits to the minimum and maximum
   of displayed data.
 \item
   \texttt{'xLabel='} {[} char \textbar{} \emph{empty} {]} - Label the
   x-axis.
 \item
   \texttt{'yLabel='} {[} char \textbar{} \emph{empty} {]} - Label the
   y-axis.
 \item
   \texttt{'zeroLine='} {[} \texttt{true} \textbar{}
   \emph{\texttt{false}} {]} - (Inheritable) Add a horizontal zero line
   if zero is included on the y-axis.
 \end{itemize}
 
 \paragraph{Generic options}
 
 See help on \href{report/Contents}{generic options} in report objects.
 
 \paragraph{Description}
 
 \paragraph{Example}


