

    \filetitle{plotcmp}{Comparison graph for two time series}{tseries/plotcmp}

	\paragraph{Syntax}
 
 \begin{verbatim}
 [Ax,Lhs,Rhs] = plotcmp(X,...)
 [Ax,Lhs,Rhs] = plotcmp(Range,X,...)
 \end{verbatim}
 
 \paragraph{Input arguments}
 
 \begin{itemize}
 \item
   \texttt{Range} {[} numeric {]} - Date range; if not specified the
   entire range of the input tseries object will be plotted.
 \item
   \texttt{X} {[} tseries {]} - Tseries object with two or more columns;
   the difference (between the second and the first column (or any other
   linear combination of its columns specified through the option
   \texttt{'compare='}) will be displayed as an RHS area or bar graph.
 \end{itemize}
 
 \paragraph{Output arguments}
 
 \begin{itemize}
 \item
   \texttt{Ax} {[} numeric {]} - Handles to the LHS and RHS axes.
 \item
   \texttt{Lhs} {[} numeric {]} - Handles to the two original lines.
 \item
   \texttt{Rhs} {[} numeric {]} - Handles to the area or bar difference
   graph.
 \end{itemize}
 
 \paragraph{Options}
 
 \begin{itemize}
 \item
   \texttt{'compare='} {[} numeric \textbar{} \emph{\texttt{{[}-1;1{]}}}
   {]} - Linear combination of the observations that will be plotted in
   the RHS graph;
   \texttt{{[}-1;1{]} means a difference between the second series and the first series,}X\{:,2\}-X\{:,1\}`.
 \item
   \texttt{'cmpColor='} {[} numeric \textbar{}
   \emph{\texttt{{[}1,0.75,0.75{]}}} {]} - Color that will be used to
   plot the area or bar difference (comparison) graph.
 \item
   \texttt{'cmpPlotFunc='} {[} \texttt{@area} \textbar{}
   \emph{\texttt{@bar}} {]} - Function that will be used to plot the
   difference (comparision) data on the RHS.
 \end{itemize}
 
 See help on \url{tseries/plotyy} for other options available.
 
 \paragraph{Description}
 
 \paragraph{Example}


