

    \filetitle{plotyy}{Line plot function with LHS and RHS axes for time series}{tseries/plotyy}

	\paragraph{Syntax}
 
 \begin{verbatim}
 [Ax,Lhs,Rhs,Range] = plotyy(X,Y,...)
 [Ax,Lhs,Rhs,Range] = plotyy(Range,X,Y,...)
 \end{verbatim}
 
 \paragraph{Input arguments}
 
 \begin{itemize}
 \item
   \texttt{Range} {[} numeric {]} - Date range; if not specified the
   entire range of the input tseries object will be plotted.
 \item
   \texttt{X} {[} tseries {]} - Input tseries object whose columns will
   be plotted and labelled on the LHS.
 \item
   \texttt{Y} {[} tseries {]} - Input tseries object whose columns will
   be plotted and labelled on the RHS.
 \end{itemize}
 
 \paragraph{Output arguments}
 
 \begin{itemize}
 \item
   \texttt{Ax} {[} numeric {]} - Handles to the LHS and RHS axes.
 \item
   \texttt{Lhs} {[} numeric {]} - Handles to series plotted on the LHS
   axis.
 \item
   \texttt{Rhs} {[} numeric {]} - Handles to series plotted on the RHS
   axis.
 \item
   \texttt{Range} {[} numeric {]} - Actually plotted date range.
 \end{itemize}
 
 \paragraph{Options}
 
 \begin{itemize}
 \item
   \texttt{'conincident='} {[} \texttt{true} \textbar{}
   \emph{\texttt{false}} {]} - Make the LHS and RHS y-axis grids
   coincident.
 \item
   \texttt{'dateFormat='} {[} char \textbar{}
   \emph{irisget(`plotdateformat')} {]} - Date format for the tick marks
   on the x-axis.
 \item
   \texttt{'dateTick='} {[} numeric \textbar{} \emph{\texttt{Inf}} {]} -
   Vector of dates locating tick marks on the x-axis; Inf means they will
   be created automatically.
 \item
   \texttt{'freqLetters='} {[} char \textbar{} \emph{`YHQBM'} {]} - Five
   letters to represent the five date frequencies (yearly, half-yearly,
   quarterly, bi-monthly, and monthly).
 \item
   \texttt{'lhsPlotFunc='} {[} @area \textbar{} @bar \textbar{}
   \emph{@plot} \textbar{} @stem {]} - Function that will be used to plot
   the LHS data.
 \item
   \texttt{'lhsTight='} {[} \texttt{true} \textbar{}
   \emph{\texttt{false}} {]} - Make the LHS y-axis tight.
 \item
   \texttt{'rhsPlotFunc='} {[} @area \textbar{} @bar \textbar{}
   \emph{@plot} \textbar{} @stem {]} - Function that will be used to plot
   the RHS data.
 \item
   \texttt{'rhsTight='} {[} \texttt{true} \textbar{}
   \emph{\texttt{false}} {]} - Make the RHS y-axis tight.
 \end{itemize}
 
 \paragraph{Description}
 
 \paragraph{Example}


