
    \foldertitle{dates}{Dates and date ranges}{dates/Contents}

	\paragraph{Creating IRIS serial date numbers}
 
 \begin{itemize}
 \item
   \href{dates/bb}{\texttt{bb}} - IRIS serial date numbers for dates with
   bi-monthly frequency.
 \item
   \href{dates/bbtoday}{\texttt{bbtoday}} - IRIS serial date number for
   current bi-month.
 \item
   \href{dates/hh}{\texttt{hh}} - IRIS serial date numbers for dates with
   half-yearly frequency.
 \item
   \href{dates/hhtoday}{\texttt{hhtoday}} - IRIS serial date number for
   current half-year.
 \item
   \href{dates/mm}{\texttt{mm}} - IRIS serial date numbers for dates with
   monthly frequency.
 \item
   \href{dates/mmtoday}{\texttt{mmtoday}} - IRIS serial date number for
   current month.
 \item
   \href{dates/qq}{\texttt{qq}} - IRIS serial date numbers for dates with
   quarterly frequency.
 \item
   \href{dates/qqtoday}{\texttt{qqtoday}} - IRIS serial date number for
   current quarter.
 \item
   \href{dates/yy}{\texttt{yy}} - IRIS serial date numbers for dates with
   yearly frequency.
 \item
   \href{dates/yytoday}{\texttt{yytoday}} - IRIS serial date number for
   current year.
 \end{itemize}
 
 \paragraph{Computing special dates (daily dates only)}
 
 \begin{itemize}
 \item
   \href{dates/datbom}{\texttt{datbom}} - Beginning of month for the
   specified daily date.
 \item
   \href{dates/datboq}{\texttt{datboq}} - Beginning of quarter for the
   specified daily date.
 \item
   \href{dates/datboy}{\texttt{datboy}} - Beginning of year for the
   specified daily date.
 \item
   \href{dates/dateom}{\texttt{dateom}} - End of month for the specified
   daily date.
 \item
   \href{dates/dateoq}{\texttt{dateoq}} - End of quarter for the
   specified daily date.
 \item
   \href{dates/dateoy}{\texttt{dateoy}} - End of year for the specified
   daily date.
 \end{itemize}
 
 \paragraph{Creating date ranges}
 
 \begin{itemize}
 \item
   \href{dates/daterange}{\texttt{daterange}} - Use the colon operator to
   create date ranges.
 \item
   \href{dates/datxtick}{\texttt{datxtick}} - Change ticks, labels and/or
   date frequency on x-axis in existing tseries graphs.
 \end{itemize}
 
 \paragraph{Converting dates}
 
 \begin{itemize}
 \item
   \href{dates/clp2dat}{\texttt{clp2dat}} - Convert text in system
   clipboard to dates.
 \item
   \href{dates/dat2char}{\texttt{dat2char}} - Convert dates to character
   array.
 \item
   \href{dates/dat2charlist}{\texttt{dat2charlist}} - Convert dates to a
   comma-separated list.
 \item
   \href{dates/dat2clp}{\texttt{dat2clp}} - Convert dates to text and
   paste to system clipboard.
 \item
   \href{dates/dat2dec}{\texttt{dat2dec}} - Convert dates to their
   decimal representations.
 \item
   \href{dates/dat2str}{\texttt{dat2str}} - Convert IRIS dates to cell
   array of strings.
 \item
   \href{dates/dat2ypf}{\texttt{dat2ypf}} - Convert IRIS serial date
   number to year, period and frequency.
 \item
   \href{dates/dec2dat}{\texttt{dec2dat}} - Convert decimal numbers to
   IRIS serial date numbers.
 \item
   \href{dates/str2dat}{\texttt{str2dat}} - Convert strings to IRIS
   serial date numbers.
 \end{itemize}
 
 \paragraph{Date comparison}
 
 \begin{itemize}
 \item
   \href{dates/datcmp}{\texttt{datcmp}} - Compare two IRIS serial date
   numbers.
 \item
   \href{dates/datdiff}{\texttt{datdiff}} - Number of periods between two
   dates with check for date frequency.
 \item
   \href{dates/rngcmp}{\texttt{rngcmp}} - Compare two IRIS date ranges.
 \end{itemize}
 
 \paragraph{Getting on-line help on date functions}
 
 \begin{verbatim}
 help dates
 help dates/function_name
 \end{verbatim}



